{\normalsize \textbf{Vagueness and imprecise imitation in signalling games}}

### 2016-06-05 paper/version_final/paper.tex
added footnote and references on stochastic game theory

The next section introduces the background against which the work presented here can be
appreciated. Section~\ref{sec:repl-diff-dynam} introduces a generalisation of the replicator
dynamic which is derived from the idea that agents imitate other agents' behaviour while
possibly confusing similar states. This imprecise imitation dynamic is explored in
Section~\ref{sec:exploring-rdd}. Section~\ref{sec:discussion} reflects and compares our
approach to others. Appendix~\ref{sec:formal-stuff} provides formal detail.

>>>>

The next section introduces the background against which the work presented here can be
appreciated. Section~\ref{sec:repl-diff-dynam} introduces a generalisation of the replicator
dynamic which is derived from the idea that agents imitate other agents' behaviour while
possibly confusing similar states.\footnote{Much previous work has investigated the interplay
  of adaptive dynamics, including imitation-based update protocols, on the one hand, and noise
  or mutation, on the other hand (e.g., \citealtbjps{FosterYoung1990:Stochastic-Evol};
  \citealtbjps{FudenbergHarris1992:Evolutionary-Dy};
  \citealtbjps{KandoriMailath1993:Learning-Mutati}; \citealtbjps{Young1993:The-Evolution-o};
  \citealtbjps{FudenbergImhof2006:Imitation-Proce}). While this line of research often looks at
  finite populations and the extreme long-term behavior of the system under generic randomness,
  the focus here is on a quite particular source of stochastic noise and its quite particular
  role in the evolution of meanings through signalling.}  This imprecise imitation dynamic is
explored in Section~\ref{sec:exploring-rdd}. Section~\ref{sec:discussion} reflects and compares
our approach to others. Appendix~\ref{sec:formal-stuff} provides formal detail.
